High Resolution Time of Flight Mass Spectrometer for Measuring Products in Heterogenous Catalysis in Higly Sensitive Microreactors

### 2012-03-27 paper.tex
Various corrections
A number of suggestions and corrections was put into the
paper. The corrections are not clearly marked, need to
look at the diff.... sorry....

\author{T. Andersen}
\author{R. Jensen}
\author{....}
\affiliation{Department of Physics, Danish National Research Foundation's Center for Individual Nanoparticle Functionality (CINF), Technical University of Denmark, Building 312, DK-2800 Kgs. Lyngby, Denmark}
\author{O. Hansen}
\affiliation{Department of Micro- and Nanotechnology, Technical University of Denmark, DTU Nanotech Building 345 East, DK-2800 Kgs. Lyngby, Denmark}
\author{I. Chorkendorff}
\email[]{ibchork@fysik.dtu.dk}
\affiliation{Department of Physics, Danish National Research Foundation's Center for Individual Nanoparticle Functionality (CINF), Technical University of Denmark, Building 312, DK-2800 Kgs. Lyngby, Denmark}
%\homepage[]{Your web page}
%\thanks{}
%\altaffiliation{}
%\affiliation{}

@@

% Body of paper goes here. Use proper sectioning commands. 
% References should be done using the \cite, \ref, and \label commands
\section{Introduction}
In heterogeneous catalysis the optimization and development of equipment is important both to minimize the cost of equipment but also to be able to study complicated systems. As a platform for testing heterogeneous catalysts microfabricated reactors or microreactors have been found suitable due to both high surface-to-volume ratio, fast temperature response and minimization of thermal and concentration gradients. Such a platform have been developed in our department \cite{Henriksen2009}. However, a suitable reactor platform is only part of the task; reactant and product detection and characterization is essential to determine catalyst performance. Typically, quadrupole mass spectrometers (QMSs) are used in low pressure regimes to analyze gas composition while gas chromatographs are used for high pressure measurements. The QMS, however, suffer from a low mass resolution ($\Delta$m/m$\sim$200) which makes analysis of complicated spectra difficult and cumbersome. The QMS is additionally subject to a low mass range (typically up to $\sim$500\,amu) limiting general use. Furthermore, QMSs are typically operated by logging a single (or a few) masses as a function of time to increase time resolution. This in turn limits the ability to acquire full mass spectra continuously during the experiment. Gas chromatographs have inherently low time resolution which make them unsuitable for fast time response measurements as in the case of microreactors and is in general difficult to use as mass spectrometers. As an alternative to the gas chromatography or QMSs, time of flight mass spectrometers (TOF-MS) offer both high mass resolution ($\Delta$m/m$>$400) and fast acquisition of full mass spectra ($>$1\,Hz) along with mass range only limited by the detector. For a typical microchannel plate (MCP) a mass range of (0--5000\,amu) can be obtained. Until now, to our knowledge, the testing of catalysts in a microreactor with subsequent gas analysis by a TOF-MS have not been demonstrated. Here we describe a microreactor and TOF-MS system which combines the high sensitivity of microreactors and the high mass resolution TOF-MSs for testing and characterizing heterogeneous catalysts.

@@

\subsubsection{The microreactor platform}
Catalyst characterization and performance evaluation was performed in a microreactor platform \cite{Henriksen2009}. The microreactors are fabricated in silicon and measures 20x15\,mm. The reactor consists of two gas inlets, a gas outlet, a reactor volume and a capillary used for probing the gas from the reactor volume. The reactor volume is 3\,$\mu$m deep and 1 cm in diameter corresponding to a 240\,nL volume. The two gas inlets are combined on the chip where the inlet gases mix by diffusion. The capillary is designed such that approximately $3\cdot10^{14}$\,molecules$\cdot$s$^{-1}$ is probed from the reactor volume when operated at 1\,bar. Any surplus of gas from the two inlets that does not enter the reactor volume is directed through the outlet to a turbo pump. The design ensures that all molecules or atoms entering the reactor volume, hence exposed to the catalyst under investigation, is detected by mass spectrometry ensuring high sensitivity.

@@

\subsection{Time of flight}
The time of flight equipment used for detection of gas molecules flowed through the capillary of the microreactor is designed as an orthogonal mass spectrometer. The TOF-MS is assembled from modules purchased from Jordan TOF Products, Inc.

Ionized ions enter the source through a series of entry Einzel lenses used for focusing the beam hence minimizing divergence. In the source the beam is pushed into the flight tube by an the initial repelling push voltage, V$_p$. The ions are further accelerated from ground potential to the liner potential, V$_L$, which is the drift voltage of the flight tube. At the end of the flight tube a reflectron is installed which has two primary purposes. The effective drift length is increased hence increasing resolution of the TOF-MS. The reflectron also works as a focusing lens compensating for any initial velocity dispersion of the ions, i.e. ions with an initial higher velocity will have an increased flight length compared to slower ions. The microchannel plate (MCP) used for ion detection is placed in the focal point of the reflectron giving maximum compensation for initial velocity dispersion. The theoretical resolution of the equipment is $\Delta$m/m$\sim$4000.

In Figure \ref{fig:untreated_data} an example spectrum of a methanol and atmospheric air mixture is shown. Here the high resolution of the TOF-MS is demonstrated by resolution of methanol (CH$_3$OH) and molecular oxygen (O$_2$) which have a mass difference of 43\,milliamu.
\begin{figure}
 \includegraphics[width=16cm]{untreated_data.png}%
 \caption{Raw data acquired from the TOF-MS in a gas mixture of methanol and atmospheric air. Subfigures show the three different regions of the spectrum. From the first subfigure a delay of the approximately 150\,ns can be seen which is due to delays in cables and the rise time of the repeller pulser. From the center subfigure it is evident that 1\,amu corresponds to approximately 350\,ns difference in flight time in our system. From the last subfigure a zoom of the methanol and molecular oxygen (43\,milliamu mass difference) region is shown.\label{fig:untreated_data}}%
\end{figure}

\subsubsection{Ionization of gas}
As ionization source of the gas flow from the microreactor capillary a modified nude UHV Bayard-Alpert ion gauge is used. Approximately 3\,A is run through the filament resulting in 10\,mA emission current. The grid is biased approximately 40\,V negative compared to the filament to accelerate electrons emitted from the filament towards the grid. Contrary to standard operation of a ion gauge the collector in the center of the grid is short-circuited to the grid ensuring homogeneous field distribution within the grid. To allow ionized ions to escape from the gauge the lid of the grid has been removed \cite{Nottingham1955}. Using this configuration approximately half of the ionized ions are expected to leave the ionization gauge. The entire construction is placed in a nozzle which is differentially pumped by a turbo pump. Large amounts of gas can hence be dosed locally around the ion gauge while still maintaining a low pressure in the source region of the TOF-MS. The nozzle is essential in the setup to avoid high pressure in the source region resulting in a increase in dead counts on the MCP thus decreasing the noise to signal ratio of the recorded signal.

\subsubsection{Data treatment}
Raw data plotted with accompanying gaussian fits are shown in Figure \ref{fig:gaussian_fit}. Here the closely lying peaks from OH$^{+}$ from cracking of both residue water and water as reaction product and uncombusted NH$_3^{+}$ is shown. The ability to separate these contributions substantially simplifies quantification of the ammonia and allows for easier characterization of catalysts. 
\begin{figure}
 \includegraphics[width=14cm]{ammonia_OH_gauss_fit.png}%
 \caption{Example of two gaussian fits to a double peak consisting of NH$_{3}^{+}$ and OH$^{+}$ both at approximately 17\,amu demonstrating the resolution of the TOF-MS. The entire graph section represents a mass difference of 100\,m-amu.\label{fig:gaussian_fit}}%
\end{figure}
In Figure \ref{fig:dynamic_range} raw data from water, hydrogen and oxygen from three different regions is shown illustrating the dynamic range of the TOF-MS. At constant MCP voltage all the peaks are clearly visible although the ratio of the oxygen to water amplitude is $\sim$400. 
\begin{figure}
 \includegraphics[width=14cm]{dynamic_range.png}%
 \caption{Gaussian fits to three different mass to charge ratios from the same mass spectrum. As seen from the response a high dynamic range of the TOF-MS all yielding good gaussian fits. The TOF-MS can hence be used to monitor both very small and very large signal masses with high time resolution.\label{fig:dynamic_range}}%
\end{figure}
The dynamic range of the TOF-MS is hence comparable to the dynamic range offered by a QMS at constant preamplifier range. From Figure \ref{fig:dynamic_range} the dynamic range is estimated to $\sim$1000. Her ville jeg gerne skrive noget mere. Nogen ideer...?

\section{Oxidation of ammonia}
To demonstrate the system capability ammonia oxidation on platinum thin films has been used as test reaction. The catalytic oxidation of ammonia can proceed along primarily three different routes.
\begin{equation}
4NH_3+3O_2\rightarrow 2N_2 + 6H_2O
\label{eq:Pt_clean_combustion}
\end{equation}
\begin{equation}
2NH_3+2O_2\rightarrow N_2O + 3H_2O
\end{equation}
\begin{equation}
4NH_3+5O_2\rightarrow 4NO + 6H_2O
\end{equation}
All of these systems are difficult to analyze both qualitatively and quantitatively by due to the overlap of NH$_3$, which is a reactant, and OH$^+$ originating from cracking of H$_2$O, which is a product from the combustion, and cracking from water in the residue gas. Specifically, hydroxyls (OH$^{+}$) from cracking of trace water in the system and the combustion reaction and the primary peak of ammonia (NH$_{3}^{+}$) is both detected at m/q$\simeq$17. Without adequate mass resolution is not possible to separate the two contributions resulting in difficult analysis. Often a charge to mass ratio without cracking from either products or residue gas in the system is used to quantify the amount of ammonia and water. In the case of ammonia, m/q=15 or m/q=8.5 is typically chosen. The monitoring of other than the primary mass to charge ratio, which in the case of ammonia is m/q=17, due to mass overlap is generally not wanted due to a lower signal to noise ratio of cracking masses. This in turns affect the detection limit of the given mass. Due the acquisition of entire mass spectra with high mass resolution instead of monitoring individual masses by the TOF-MS is not limited to unique signature masses resulting in higher signal to noise ratio spectra.

At experiment start the microreactor is equilibrated with NH$_3$ and O$_2$ in a 5:3 stoichiometry (did we run at stoichiometry??). After equilibration the temperature is increased in steps from room temperature til 190\,$^{\circ}$C. The gas composition in the microreactor is continuously probed by the TOF-MS which is connected to the capillary of the microreactor.
\begin{figure}
 \includegraphics[width=14cm]{ammonia_reactivity.png}%
 \caption{Ammonia oxidation as a function of temperature on a Pt thin film. As the temperature is increased ammonia is oxidized to H$_2$O and N$_2$. Furthermore, the OH and NH$_3$ signal is anticorrelated demonstrating the ability to resolve these two close lying masses.\label{fig:ammonia_reactivity}}%
\end{figure}
In Figure \ref{fig:ammonia_reactivity} the integrated N$_2$, NH$_3$, H$_2$O, O$_2$ and OH peaks acquired from the raw TOF-MS spectrum as a function of temperature are shown. At each individual temperature step a mass scan is performed from the triggering of the acceleration pulse up to 25\,$\mu$s of flight time corresponding to a maximum of 70 amu. As seen from Figure \ref{fig:ammonia_reactivity} the combustion of NH$_3$ increases substantially at approximately 140\,$^{\circ}$C. The combustion of ammonia to molecular nitrogen and water at this temperature agrees well with literature \cite{Imbihl2007,Zeng2009}. In Figure \ref{fig:ammonia_reactivity} an anticorrelation between OH$^{+}$ and NH$_3^+$ is seen. The inverse relation between these two masses suggests that these peaks are resolved in the mass spectrum which is further strengthened by the correlation between H$_2$O$^{+}$.

@@

As a demonstration of the system ammonia oxidation on platinum thin films was performed. The ability to resolve OH$^{+}$ and NH$_3^+$ was demonstrated which is separated by 23\,milli-amu. The resolution of reactants and products enables simple and straightforward quantification of the ammonia and water signal. This greatly simplifies the analysis compared to conventional QMSs used for gas analysis. The setup is furthermore superior to conventional QMSs where the mass range is limited to $\sim$500\,amu.

>>>>

\author{T. Andersen}
\author{R. Jensen}
\author{M. K. Christensen}
\affiliation{Department of Physics, Danish National Research Foundation's Center for Individual Nanoparticle Functionality (CINF), Technical University of Denmark, Building 312, DK-2800 Kgs. Lyngby, Denmark}
\author{T. Pedersen}
\author{O. Hansen}
\affiliation{Department of Micro- and Nanotechnology, Technical University of Denmark, DTU Nanotech Building 345 East, DK-2800 Kgs. Lyngby, Denmark}
\author{I. Chorkendorff}
\email[]{ibchork@fysik.dtu.dk}
\affiliation{Department of Physics, Danish National Research Foundation's Center for Individual Nanoparticle Functionality (CINF), Technical University of Denmark, Building 312, DK-2800 Kgs. Lyngby, Denmark}
%\homepage[]{Your web page}
%\thanks{}
%\altaffiliation{}
%\affiliation{}

@@

% Body of paper goes here. Use proper sectioning commands. 
% References should be done using the \cite, \ref, and \label commands
\section{Introduction}
In heterogeneous catalysis the optimization and development of equipment is important both to minimize the cost of equipment but also to be able to study complicated systems. As a platform for testing heterogeneous catalysts microfabricated reactors or microreactors have been found suitable due to both high surface-to-volume ratio, fast temperature response and minimization of thermal and concentration gradients. Such a platform have been developed in our department \cite{Henriksen2009}. However, a suitable reactor platform is only part of the task; reactant and product detection and characterization is essential to determine catalyst performance. Typically, quadrupole mass spectrometers (QMSs) are used in low pressure regimes to analyze gas composition while gas chromatographs are used for high pressure measurements. The QMS, however, suffer from a low mass resolution ($\Delta$m/m$\sim$m up to m$\sim$200) which makes analysis of complicated spectra difficult and cumbersome. The QMS is additionally subject to a low mass range (typically $\sim$100-200\,amu) limiting general use. Furthermore, QMSs are typically operated by logging a single (or a few) masses as a function of time to increase time resolution. This in turn limits the ability to acquire full mass spectra continuously during the experiment and thus the operator before the experiments needs to decide which masses is interesting, and thus might miss interesting features in other masses. Gas chromatographs have inherently low time resolution which make them unsuitable for fast time response measurements as in the case of microreactors and is in general difficult to use as mass spectrometers. As an alternative to the gas chromatography or QMSs, time of flight mass spectrometers (TOF-MS) offer both high mass resolution ($\Delta$m/m$>$1000) and fast acquisition of full mass spectra ($>$1\,Hz) along with mass range only limited by the detector. For a reasonobly good microchannel plate (MCP) a mass range of 0--5000\,amu can be obtained. Until now, to our knowledge, the testing of catalysts in a microreactor with subsequent gas analysis by a TOF-MS have not been demonstrated. Here we describe a microreactor and TOF-MS system which combines the high sensitivity of microreactors and the high mass resolution TOF-MSs for testing and characterizing heterogeneous catalysts.

@@

\subsubsection{The microreactor platform}
Catalyst characterization and performance evaluation was performed in a microreactor platform \cite{Henriksen2009}. The microreactors are fabricated in silicon and measures 20x15\,mm. The reactor consists of two gas inlets, a gas outlet, a reactor volume and a capillary used for probing the gas from the reactor volume. The reactor volume is 3\,$\mu$m deep and 1 cm in diameter corresponding to a 240\,nL volume. The two gas inlets are combined on the chip where the inlet gases mix by diffusion. The capillary is designed such that approximately $3\times10^{14}$\,molecules$\cdot$s$^{-1}$ is probed from the reactor volume when operated at 1\,bar. Any surplus of gas from the two inlets that does not enter the reactor volume is directed through the outlet to a turbo pump. The design ensures that all molecules or atoms entering the reactor volume, hence exposed to the catalyst under investigation, is detected by mass spectrometry ensuring high sensitivity.

@@

\subsection{Time of flight}
SKAL VI SKRIVE LIDT OM SELVE KAMMERET (baggrundstryk, pumpetyper, etc...)

The time of flight equipment used for detection of gas molecules flowed through the capillary of the microreactor is designed as an orthogonal mass spectrometer. The TOF-MS is assembled from modules purchased from Jordan TOF Products, Inc.

Ionized ions enter the source through a series of entry Einzel lenses used for focusing the beam hence minimizing divergence. In the source the beam is pushed into the flight tube by an the initial repelling push voltage, $V_p$. The ions are further accelerated from ground potential to the liner potential, $V_L$, and the drift velocity of an ion starting exactly from the center of the accelration region is thus $V_L + V_p/2$. At the end of the flight tube a reflectron is installed which has two primary purposes. The effective drift length is increased hence increasing resolution of the TOF-MS. The reflectron also works as a focusing lens compensating for any initial velocity dispersion of the ions, i.e. ions with an initial higher velocity will have an increased flight length compared to slower ions. The microchannel plate (MCP) used for ion detection is placed in the focal point of the reflectron giving maximum compensation for initial velocity dispersion. The theoretical resolution of the equipment is $\Delta$m/m$\sim$4000.

In Figure \ref{fig:untreated_data} an example spectrum of a methanol and atmospheric air mixture is shown. Here the high resolution of the TOF-MS is demonstrated by resolving of methanol (CH$_3$OH) and molecular oxygen (O$_2$) which have a mass difference of 43\,milliamu.
\begin{figure}
 \includegraphics[width=16cm]{untreated_data.png}%
 \caption{Raw data acquired from the TOF-MS in a gas mixture of methanol and atmospheric air. Subfigures show the three different regions of the spectrum. From the first subfigure a delay of approximately 150\,ns can be seen which is due to delays in cables and the rise time of the repeller pulser. In the center subfigure the extremely good seperation between seperate masses is shown. It is evident that 1\,amu corresponds to approximately 350\,ns difference in flight time in our system in the mass regime around 20\,amu. In the last subfigure a zoom of the methanol and molecular oxygen (43\,milliamu mass difference) region is shown.\label{fig:untreated_data}}%
\end{figure}

\subsubsection{Ionization of gas}
As ionization source of the gas flow from the microreactor capillary a modified nude UHV Bayard-Alpert ion gauge is used. Approximately 3\,A is run through the filament resulting in 10\,mA emission current. The grid is biased approximately 40\,V negative compared to the filament to accelerate electrons emitted from the filament towards the grid. Contrary to standard operation of a ion gauge the collector in the center of the grid is short-circuited to the grid ensuring homogeneous field distribution within the grid. To allow ionized ions to escape from the gauge the lid of the grid has been removed \cite{Nottingham1955}. Using this configuration approximately half of the ionized ions are expected to leave the ionization gauge. The entire construction is placed in a nozzle which is differentially pumped by a turbo pump. Large amounts of gas can hence be dosed locally around the ion gauge while still maintaining a low pressure in the source region of the TOF-MS. The nozzle is essential in the setup to avoid high pressure in the acceleration region and drift tube resulting in an increase in dead counts on the MCP thus decreasing the signal-to-noise ratio of the recorded signal.

\subsubsection{Data treatment}
Raw data plotted with accompanying gaussian fits are shown in Figure \ref{fig:gaussian_fit}. Here the closely lying peaks from OH$^{+}$ from cracking of both residue water and water as reaction product and uncombusted NH$_3^{+}$ is shown. The ability to separate these contributions substantially simplifies quantification of the ammonia and allows for easier characterization of catalysts. 
\begin{figure}
 \includegraphics[width=14cm]{ammonia_OH_gauss_fit.png}%
 \caption{Example of two gaussian fits (dashed red lines) and the sum of the two fits (green solid line) to a double peak consisting of NH$_{3}^{+}$ and OH$^{+}$ both at approximately 17\,amu demonstrating the resolution of the TOF-MS. The entire graph section represents a mass difference of 100\,m-amu.\label{fig:gaussian_fit}}%
\end{figure}
In Figure \ref{fig:dynamic_range} raw data from water, hydrogen and oxygen from three different regions is shown illustrating the dynamic range of the TOF-MS. At constant MCP voltage all the peaks are clearly visible although the ratio of the oxygen to water amplitude is $\sim$400. 
\begin{figure}
 \includegraphics[width=14cm]{dynamic_range.png}%
 \caption{Gaussian fits to three different mass to charge ratios from the same mass spectrum (integrated area indicated in each panel). As seen from the response a high dynamic range of the TOF-MS all yielding good gaussian fits. The TOF-MS can hence be used to monitor both very small and very large signal masses with high time resolution.\label{fig:dynamic_range}}%
\end{figure}
In reallity the dynamic range is limited mostly by the data aquisition hardware as well as the quality of the ion-source. Even with our very simple home-build ionization source and a rather modest 8-bit digitizer, the dynamic range is from Figure~\ref{fig:dynamic_range} estimated to be $\sim$1000 using an integration time of $\sim5\,$s. The dynamic range of the TOF-MS is hence comparable to the dynamic range offered by a QMS at constant preamplifier range, while covering a much larger mass range.

SKAL VI SKRIVE NOGET OM FLYVETID-TIL-MASSE OMREGNING?

\section{Oxidation of ammonia}
To demonstrate the system capability ammonia oxidation on platinum thin films has been used as test reaction. The catalytic oxidation of ammonia can proceed along primarily three different routes.
\begin{equation}
4NH_3+3O_2\rightarrow 2N_2 + 6H_2O
\label{eq:Pt_clean_combustion}
\end{equation}
\begin{equation}
2NH_3+2O_2\rightarrow N_2O + 3H_2O
\end{equation}
\begin{equation}
4NH_3+5O_2\rightarrow 4NO + 6H_2O
\end{equation}
All of these systems are difficult to analyze both qualitatively and quantitatively due to the overlap of NH$_3$, which is a reactant, and OH$^+$ originating from cracking of H$_2$O, which is a product from the combustion and is a part of the residue gas. Specifically, hydroxyls (OH$^{+}$) from cracking of trace water in the system and the combustion reaction and the primary peak of ammonia (NH$_{3}^{+}$) is both detected at m/q$\simeq$17. Without adequate mass resolution it is not possible to separate the two contributions resulting in difficult analysis. Often a charge to mass ratio without cracking from either products or residue gas in the system is used to quantify the amount of ammonia and water. In the case of ammonia, m/q=15 or m/q=8.5 is typically chosen since water does not contribute to these masses. However both of these masses contains only a very small fraction of the main peak, since it involves either the loss of two hydrogen atoms or a double charged ammonia molecule, both processes have very low yields. Thus the measurement of these masses have a very poor signal to noise ratio, making measurements on ammonia very difficult with tradition mass spectrometry methods.

At experiment start the microreactor is equilibrated with NH$_3$ and O$_2$ in a 5:3 stoichiometry (did we run at stoichiometry??). After equilibration the temperature is increased in steps from room temperature til 190\,$^{\circ}$C. The gas composition in the microreactor is continuously probed by the TOF-MS which is connected to the capillary of the microreactor.
\begin{figure}
 \includegraphics[width=14cm]{ammonia_reactivity.png}%
 \caption{Ammonia oxidation as a function of temperature on a Pt thin film. As the temperature is increased ammonia is oxidized to H$_2$O and N$_2$. Furthermore, the OH and NH$_3$ signal is anticorrelated demonstrating the ability to resolve these two close lying masses.\label{fig:ammonia_reactivity}}%
\end{figure}
In Figure \ref{fig:ammonia_reactivity} the integrated N$_2$, NH$_3$, H$_2$O, O$_2$ and OH peaks acquired from the raw TOF-MS spectrum as a function of temperature are shown. At each individual temperature step a mass scan is performed from the triggering of the acceleration pulse up to 25\,$\mu$s of flight time corresponding to a maximum of 70 amu. As seen from Figure \ref{fig:ammonia_reactivity} the combustion of NH$_3$ increases substantially at approximately 140\,$^{\circ}$C. The combustion of ammonia to molecular nitrogen and water at this temperature agrees well with literature \cite{Imbihl2007,Zeng2009}. In Figure \ref{fig:ammonia_reactivity} an anticorrelation between OH$^{+}$ and NH$_3^+$ is seen. The inverse relation between these two masses can only be measured because these peaks are resolved in the mass spectrum. As expected a strong correlation between H$_2$O$^{+}$ and OH$^+$ is seen.

@@

As a demonstration of the system ammonia oxidation on platinum thin films was performed. The ability to resolve OH$^{+}$ and NH$_3^+$ which is separated by 23\,milli-amu was demonstrated. The resolution of reactants and products enables simple and straightforward quantification of the ammonia and water signal. This greatly simplifies the analysis compared to conventional QMSs used for gas analysis. The setup is furthermore superior to conventional QMSs where the mass range is limited to $\sim$500\,amu.
